---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bezieR

<!-- badges: start -->
<!-- badges: end -->

The goal of bezieR is to It helps visually analyze Bezier curves and animate their construct function of $f(t)$. It was inspired by [Wikipedia visualization] (https://en.wikipedia.org/wiki/B%C3%A9zier_curve#/media/File:B%C3%A9zier_2_big.gif)

# BezieR
`bezieR` is an R package designed for Bezier curves analysis. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Hussain-Alsalman/bezieR")
```
## Example

This is a basic example which shows visualize the relationsip between the control points $P_n$of Bezier curve a common problem:

```{r example}
library("bezieR")
## basic example code
analyze_bezier(cp_x =c(10,20,30), cp_y = c(10,50,10))
```

You can get an intiution about the control points and Bezier curves relationship by animating the path of the curve

```{r}
animate_bezier(cp_x =c(10,20,30), cp_y = c(10,50,10))
```

# Additional Information 

You can read my detailed [blog post](https://www.arabiananalyst.com/2020/06/28/2020-06-28-bezier-curves/) about Bezier Curves. It goes a littble bit beneth the surface and discusses some mathimatical intuitions behind these curves   

# Resource 

- The invaluable book by [@TheRealPomax](https://twitter.com/TheRealPomax)[A Primer on Bézier Curves](https://pomax.github.io/bezierinfo/)
- [NodeJS with R Integration] (https://colinfay.me/node-r-package/)
- [SVG Parser](https://github.com/hughsk/svg-path-parser)
